\documentclass[a4paper]{report}

\input{../Subfiles/Packages.tex}
\input{../Subfiles/Operators.tex}
\input{../Subfiles/Languages.tex}


\title{Master Thesis: Horn Minimization}
\author{Simon VILMIN}
\date{year 2017 - 2018}

\begin{document}
\maketitle
\tableofcontents

\chapter{Introduction and definitions}

This report summarizes the work on the Horn-minimization subject. We first give
mathematical definitions we may need for all the report, the reader may refer 
to \cite{Lat&Ord}, \cite{CExp}. The aim of this chapter is to give various 
aspects of a same object, namely an implication basis. We first go through 
logical definitions, then we move to set theoretic aspect (with closure) 

\section{Logic pov}

Note that we consider the reader to have a few background in mathematical logic,
so that the following definitions just stand as a summary and refresher. The 
reminder is only about propositional logic up to our needs.

\begin{definition}[\belemp{clause}]
	Pouet et pouf sont sur un bateau.
\end{definition}

\begin{definition}[\belemp{Horn formula}]
	
\end{definition}

\begin{definition}[\belemp{semantic entailment}]
	
\end{definition}

\section{Order theory pov}

\section{FCA pov}

\section{Closure systems pov}

In this part, we will be considering definitions of set theory, with relation to
closure systems. The reader may refer to \cite{CExp}, \cite{Lat&Ord} for more 
details and further definitions.

\begin{definition}[\belemp{Closure operator}, \belemp{closure system}] Let
$\Sigma$ be a set, and define $\phi : \Sigma \longrightarrow \Sigma$ an
application. $\phi$ is a \belemp{closure} if it has the three following
properties for all $X, Y \subseteq \Sigma$:
\begin{itemize}
	\item[(i)] $X \subseteq \phi(X)$ (\midemp{extensive})
	\item[(ii)] $X \subseteq Y \longrightarrow \phi(X) \subseteq \phi(Y)$ 
		(\midemp{monotone})
	\item[(iii)] $\phi(\phi(X)) = \phi(X)$ (\midemp{idempotent})
\end{itemize}

\noindent Then, the pair $(\Sigma, \phi)$ is called a \belemp{closure system}.
	
\end{definition}


\begin{definition}[\belemp{Closed set}] Let $(\Sigma, \phi)$ be a closure 
system. A subset $X$ of $\Sigma$ is a \belemp{closed set} (with respect to 
$\phi$) if $\phi(X) = X$. We will denote by $\Sigma_{\phi}$ the set of all 
closed sets of $(\Sigma, \phi)$, that is:
	
	\[ \Sigma_{\phi} = \left\{ X \subseteq \Sigma \; | \; \phi(X) = X 
	\right\}  \]

\noindent and $\Sigma_{\phi}$ has the following properties:
\begin{itemize}
	\item[(i)] $\Sigma \in \Sigma_{\phi}$,
	\item[(ii)] if $X, Y \in \Sigma_{\phi}$, so does $X \cap Y$ 
		(\midemp{$\Sigma_{\phi}$ is closed under intersection}).
\end{itemize}
	
\end{definition}

\noindent Note that a closure system can be characterized either by its closure
operator, or by its set of closed sets. In other words, we can derive 
$\Sigma_{\phi}$ from $\phi$, as $\phi$ from $\Sigma_{\phi}$. The closed set 
associated to $X$ is the smallest closed set containing $X$, i.e:

	\[ \phi(X) = \bigcap \{Y \in \Sigma_\phi \; | \; X \subseteq Y \} \]

\noindent Since $\Sigma_{\phi}$ is closed under intersection, the resultant of
the intersection is also a closed set. The set of closed sets ordered by 
inclusion defines a complete lattice as defined previously. 


\paragraph{Example} Let $\Sigma = \llbracket 1 \; ; \; 4 \rrbracket$ and 
$\phi(X) = X \cup \{4 \}$. The pair $(\Sigma, \phi)$ is a closure system whose
closed sets are all the subsets containing 4. Let us prove that $\phi$ is indeed
a closure operator:
\begin{itemize}
	\item[(e)] for all subsets $X$ of $\Sigma$, either $4 \in X$ and 
	$\phi(X) = X \cup \{4 \} = X$ so $X \subseteq \phi(X)$, either $4 \notin X$
	and $X \subseteq X \cup \{4 \} = \phi(X)$.
	\item[(m)]
	\item[(i)] by definition $\phi(X)$ contains 4, so it will not be
	changed by applying $\phi$ another time.
\end{itemize}

\noindent Another interesting definition of $\Sigma_{\phi}$ is:

	\[ \Sigma_{\phi} = \{ \phi(X) \; | \; X \subseteq \Sigma \} \]

\noindent Then, in our example:

	\[ \Sigma_{\phi} = \{ \{ 4\}, \{ 1, 4\}, \{ 2, 4\},
		\{ 3, 4\}, \{ 1, 2, 4\}, \{ 1, 3, 4\},\{ 2, 3, 4\}, 
		\{ 1, 2, 3, 4\} \}
	\]
	
\noindent The lattice $(\Sigma_{\phi}, \subseteq)$ is:



	 
\section{Implication Basis}

\begin{definition}[\belemp{Implication}] Let $\Sg$ be a set, and $A, B 
\subseteq 
\Sg$. An \belemp{implication} over $\Sg$ is a relation/pair between $A$ and 
$B$, denoted by $A \imp B$. $A$ is the \belemp{premise}, $B$ the 
\belemp{conclusion}. 	
\end{definition}

\begin{definition}[\belemp{Model of an implication}] A subset $M \subseteq 
\Sg$ is a model of $A \imp B$, written $M \models A 
\imp B$ if $B \subseteq M \lor A \nsubseteq M$ (think of logical 
approach).
\end{definition}

\begin{definition}[\belemp{Model of an implication basis}] Let $\I$ be
a set of implication (or an \midemp{implication basis}) over $\Sg$. A subset
$M \subseteq \Sg$ is a model of $\I$ if $M \models A \imp
B$ for each $A \imp B$ in $\I$. It is denoted by $M \models \I$.
\end{definition}

The set of models of $\I$ over $\Sg$ describes a closure system $(\Sg, \phi)$. 
Then, An implication $A \imp B$ holds in $\I$ iff $B \subseteq \phi(A)$. 
Conversely, if $(\Sg, \phi)$ is a closure system, then we can define an 
implication basis $\I$ such that the models $M(\I)$ of $\I$ are the closed sets
$\Sg_\phi$ of $(\Sg, \phi)$. An implication $A \imp B$ \belemp{semantically 
follows} from $\I$ if for all $M \subseteq \Sg$ s.t $M \models \I$, we also have
$M \models A \imp B$. Then we write $\I \models A \imp B$.

\begin{definition}[\belemp{Completeness}] $\I$ over $\Sg$ is called 
\belemp{complete} with respect to a closure system if every implication holding
in the closure system follows from $\I$.
	
\end{definition}

Given $\I$, we denote by $\I(M)$ the closure of $M$ in $\I$, that is the 
smallest model of $\I$ containing $M$.

\begin{definition}[\belemp{Properties of $\I$}] Let $\I$ be a set of 
implications over $\Sg$, and $(\Sg, \phi)$ be a closure system. $\I$ is:
\begin{itemize}
	\item[(i)] \belemp{sound} if each implications of $\I$ holds in $\Sg_\phi$
	\item[(ii)] \belemp{complete} if each implications holding in $\Sg_\phi$ 
	follows from $\I$
	\item[(iii)] \belemp{nonredundant} if no implication in $\I$ follows from 
	other implications of $\I$.
\end{itemize}
	
\end{definition}

So our goal is to find such an implication basis which concentrates all possible
knowledge in the minimal number of implications. Finding (and minimizing!) such
an implication set can be very Time-Consuming.

\begin{definition}[\belemp{Pseudo-closed set}] Let $(\Sg, \phi)$ be a closure 
system. A subset $M \subseteq \Sg$ is \belemp{pseudo-closed} iff 
\begin{itemize}
	\item $\phi(M) \neq M$ ($M$ is not closed),
	\item if $Q \subset M$ is pseudo-closed, then $\phi(Q) \subseteq M$.
\end{itemize}

\end{definition}

Note that the empty set $\emptyset$ is pseudo-closed iff it is not closed. One 
can also define pseudo-closed set with help of \midemp{quasi-closed} sets. We
can prove that a pseudo-closed set is some kind of discontinuous structure 
within a lattice.

\begin{definition}[\belemp{Duquenne-Guigues Basis}] Let $(\Sg, \phi)$ be a 
closure system. The \belemp{Duquenne-Guigues} basis or \belemp{canonical} basis
$\I$ is:

	\[ \I = \{ M \imp \phi(M) \; | \; M \subseteq \Sg, \, M \;
	 	\text{pseudo-closed} \} \]
	
\noindent and $\I$ is complete, sound and nonredundant.
\end{definition}


\begin{definition}[\belemp{Preclosed set}] Given a closure system $(\Sg, \phi)$,
a subset $M \subseteq \Sg$ is \belemp{preclosed} iff it contains the closure of
all its proper preclosed subsets.
	
\end{definition}

\chapter{Algorithms}

In the first chapter we introduced the aim of our study, our working procedure
and the main tools for us to understand the next explanations. In this part, we
will focus on reviewing the existing algorithms for the Horn minimization task. 


%Maier Algorithm
\input{Algo/Maier-Algorithm.tex}

% Ausiello Graph algorithm (FD-Graph)
\input{Algo/FD-Graph-Algorithm.tex}




\section{Strong duality in Horn Minimization}

Pure Horn function (PHF). Implicates. Subsuming. Given $h$ a PHF, denote by 
$\mathcal{I}(h)$ the set of implicates of $h$. $\cal{P} \subseteq \cal{I}$ is
the set of prime implicates of $h$. Forward chaining is the closure operator. 

The essential set $\cal{E}_S$ of a subset $S$ of variables $V$ is defined as
follows:

	\[ \cal{E}_S = \{ A \imp B | A \subseteq S, B \nsubseteq S \} \]
	
It describes a subset of $h$ for which $S$ is a false point. In fact, it points
out the clauses falsified by $S$. So more than indicating whether $S$ is a model
or not of the function, it also says where does it falsify the function.

Lemma 4 states that a CNF $\phi$ represents a function $h$ if for each non-model
$S$ of $h$, $\phi$ contains at least one of the clause falsified by $h$. That is
$h$ and $\phi$ are false at the same points.

$ess(h)$ allows to partition the non-models of $h$. It is the number of maximum
pairwise disjoint essential sets of $h$. This can be viewed as the number of
subsets sufficient to disjointly describes false point of $h$. Body-disjoint 
essential set is a stronger criterion. Two essential sets $\cal{E}$, $\cal{E}'$
are body-disjoint if the intersection of the left sides they contain is empty.

sketch of proof for lemma 5. 

\begin{lemma} Let $h$ be PHF over $V$. For $P, Q \subseteq V$, we have the 
following equivalences:

\begin{itemize}
	\item[(i)] $\mathcal{E}_P$ and $\mathcal{E}_Q$ are disjoint iff $F_h(P \cap
		Q) \subseteq P \cup Q$,
	
	\item[(ii)] $\cal{E}_P$ and $\cal{E}_Q$ are body-disjoint iff $F_h(P
	 	\cap Q) \subseteq P xor Q$.
\end{itemize}
	
\end{lemma} 

\begin{proof}
(i), $\imp$. Note that for $P \subseteq V$, $F_h(P)$ is exactly the set of
variables contained in $\mathcal{E}_P \cup P$. Also, note that if $P, Q$, 
$\mathcal{E}_{P \cap Q} \subseteq \mathcal{E}_P \cap \mathcal{E}_Q$. If the
two last essential sets are disjoint, then their intersection is empty, 
leading to $\mathcal{E}_{P \cap Q} = \emptyset$. In other words, $P \cap Q$ is
a model of $h$, and by definition $F_h(P \cap Q) = P \cap Q \subseteq P \cup Q$

\vspace{1.2em}

(i), $\rimp$. Let us denote by $V(\mathcal{E}_P)$ the variables contained in 
$\mathcal{E}_P$. We reason by contraposition. Suppose $V(\mathcal{E}_{P \cap Q})
\neq \emptyset$. Then, 

\begin{align*}
	F_h(P \cap Q) & = V(\mathcal{E}_{P \cap Q}) \cup (P \cap Q) \\
	& = (V(\mathcal{E}_{P \cap Q}) \cup P) \cap
		(V(\mathcal{E}_{P \cap Q}) \cup Q) \\
	& = (A \cup X \cup P) \cap (A \cup X \cup Q) \\
	& = (P \cup X) \cap (Q \cup X) \\
	& = (P \cap Q) \cup X \nsubseteq P \cup Q
\end{align*}


\noindent where $X$ is a non-empty set derived from the definition of 
$\mathcal{E}_{P \cap Q}$ if it is non-empty. Indeed if $\mathcal{E}$ is 
non-empty then it contains at least one implication $B \imp u$ such that $B 
\subseteq P \cap Q$ and $u \notin P \cap Q$. The set of such $u$ is $X$. Note
that in this case, since $\mathcal{E}$ is derived from the essential sets of
$P$ and $Q$, $X$ does belong neither to $P$ nor $Q$. In other words $X 
\nsubseteq P \cup Q$. 

$A$ is a subset of $P \cap Q$. Indeed, it is possible not to have $P \cap Q
\subseteq V$ if the implications in $V$ only use parts of $P \cap Q$. $A$ is 
non-empty, and is be absorbed by $P$ or $Q$ in the previous derivations, 
through $P \cup A$ and $Q \cup A$. 

\vspace{1.2em}

(ii) $\imp$.
\end{proof}


\bibliographystyle{acm}
	\bibliography{Biblio.bib}

\end{document}